Hydras \& Co.

### 2024-02-13 doc/chapter-primrec.tex
minor changes in pdf doc

The example in the preceding section clearly shows that, in order to prove that a given arithmetic function
(defined in \gallina{} as usual) is primitive recursive, trying to \emph{type} a term  of type (\texttt{PrimRec $n$}) is not a good method, since such terms may be too large, even for simple arithmetic functions. The method proposed in the library \texttt{Ackermann.primRec} is the following one:

\begin{enumerate}
\item Define a type corresponding to the statements of the form  "the $n$-ary function $f$ is primitive recursive ''.
\item Prove handy lemmas which may help to prove that a given function is primitive recursive. These lemmas can be considered as a way to build \emph{silently} large terms of 
type (\texttt{PrimRec $n$}) in intermediate steps of the proof.
More, we can associate \emph{tactics} with these lemmas.

@@

The function we consider is defined and proven correct in
Module~\href{../theories/html/hydras.Hydra.Battle_length.html}{Hydra.Battle\_length}.

\input{movies/snippets/Battle_length/BattleLength}

>>>>

The example in the preceding section clearly shows that, in order to prove that a given arithmetic function
(defined in \gallina{} as usual) is primitive recursive, trying to \emph{type} a term  of type (\texttt{PrimRec $n$}) is not always a good method, since such terms may be too large, even for simple arithmetic functions. The interactive method proposed in the library \texttt{Ackermann.primRec} is the following one:

\begin{enumerate}
\item Define a type corresponding to the statements of the form  "the $n$-ary function $f$ is primitive recursive ''.
\item Prove handy lemmas which may help to prove that a given function is primitive recursive. These lemmas can be considered as a way to build \emph{silently} large terms of 
type (\texttt{PrimRec $p$})\footnote{Beware that $p$ is not always equal to $n$.} in intermediate steps of the proof.
More, we will be able to associate \emph{tactics} with these lemmas.

@@

The following lemma (from 
Module~\href{../theories/html/hydras.Hydra.Battle_length.html}{Hydra.Battle\_length}) relates the length of standard hydra battles with the $L_\alpha$ rapidly growing hierarchy (please see Sect.~\vref{sect:lalpha-section}).

\inputsnippets{Battle_length/BattleLengtha}
